NGO analysis

### 2022-07-31 Dashboard/Dashboard testing material/New dashboard file name tests.Rmd
Adding code to generate report title. Updating to v005. Updating README. Saving v004.

    # Based on code in Mastering Shiny - creating a temporary directory and file
    filename = "report.pdf",
    content = function(file) {
      tempReport <- file.path(tempdir(), "report.Rmd")
      file.copy("report.Rmd", tempReport, overwrite = TRUE)

>>>>

    # creating the file name using the NGO title and system date
    filename = function() {
      str_c(title(), "_", Sys.Date(), ".pdf")
    },
    content = function(file) {
      # Based on code in Mastering Shiny - creating a temporary directory and file
      tempReport <- file.path(tempdir(), "report.Rmd")
      file.copy("report.Rmd", tempReport, overwrite = TRUE)
